### 2012-05-10 GUIErrorDetector/paper/technique.tex
add an example figure after section 2.1 and revise the makefile

\noindent  {\textsc{\textbf{Problem.}}}
At a high level, to detect an invalid thread access error, an analysis needs to track all
non-UI threads spawned by the UI thread, and check whether those non-UI threads
may invoke a UI-accessing method.

@@

\textbf{3. Filter Reports Containing Library Calls}. A
method call chain containing certain library calls
like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
method is called when the JVM terminates, and uses multithreading
to dispose all GUI objects when the program exits.
% We encoded a list of 25 common library calls by proposing
% a basic set of library calls that seemed %natural and
% generally applicable, based on our programming experience.
% We later added other calls we found helpful in analyzing
% programs on different GUI frameworks and that we believed would be generally useful.
Our experiments use a list of 25 such library calls.
%We did this only between experiments rather than biasing experiments by tuning
%our tool to specific programs.

>>>>

\noindent  {\textsc{\textbf{Problem.}}}
At a high level, to detect an invalid thread access error, an analysis needs to track all
non-UI threads spawned by the UI thread, and check whether those non-UI threads
may invoke a UI-accessing method.\vspace{1mm}

\noindent  {\textsc{\textbf{Example.}}} Figure~\ref{fig:simplecg} shows an example call graph
to illustrate the invalid thread access problem.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.44]{simplecg}
  \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
invalid thread access problem. The \CodeIn{entry()} node is executing
in a UI thread. Nodes \CodeIn{uiAcc1()}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
three UI-Accessing methods. Node \CodeIn{safe()} is a Safe UI Method.
Node \CodeIn{start()} is a non-UI thread spawning method. Method call chain:
\CodeIn{entry()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc3()}
indicates an invalid thread access error.}}
\end{figure}

@@

\textbf{3. Filter Reports Containing Library Calls}. A
method call chain containing certain library calls
like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
method is called when the JVM terminates, and uses multithreading
to dispose all GUI objects when the program exits.
Our experiments use a list of \libnum such library calls.
